Modelling the emergence of whisker barrels

### 2020-07-09 paper/briefpaper/brief.tex
Changes one ref from a cite to a citep

\MPthreePred{To further investigate the interplay of genetic and intrinsic
  mechanisms we simulated two well known experimental manipulations of barrel
  development. First, we simulated a seminal barrel duplication paradigm}
\citep{shimogori_fibroblast_2005,assimacopoulos_fibroblast_2012}
\MPthreePred{in which the growth factor Fgf8, which is normally expressed at
  the anterior end of the cortical subplate from around E9.5}
\citep{crossley_mouse_1995}, \MPthreePred{is ectopically expressed (by
  electroporation) also at the posterior pole. We assume that this results in
  a mirror of the primary barrel cortex boundary along the rostrocaudal axis}
\cite{assimacopoulos_fibroblast_2012} \MPthreePred{and a mirroring of the
  anterior-posterior guidance gradient $\rho_1$ at the border between them
  (Fig.\,\ref{fig:fgf8}A). The result after 30000 iterations, and otherwise
  using the parameters of the example simulation, was two mirror-symmetrical
  barrel fields comprising $2N$ barrels (Fig.\,\ref{fig:fgf8}B), consistent
  with the outcome of the original experiments.}

>>>>

\MPthreePred{To further investigate the interplay of genetic and intrinsic
  mechanisms we simulated two well known experimental manipulations of barrel
  development. First, we simulated a seminal barrel duplication paradigm}
\citep{shimogori_fibroblast_2005,assimacopoulos_fibroblast_2012}
\MPthreePred{in which the growth factor Fgf8, which is normally expressed at
  the anterior end of the cortical subplate from around E9.5}
\citep{crossley_mouse_1995}, \MPthreePred{is ectopically expressed (by
  electroporation) also at the posterior pole. We assume that this results in
  a mirror of the primary barrel cortex boundary along the rostrocaudal axis}
\citep{assimacopoulos_fibroblast_2012} \MPthreePred{and a mirroring of the
  anterior-posterior guidance gradient $\rho_1$ at the border between them
  (Fig.\,\ref{fig:fgf8}A). The result after 30000 iterations, and otherwise
  using the parameters of the example simulation, was two mirror-symmetrical
  barrel fields comprising $2N$ barrels (Fig.\,\ref{fig:fgf8}B), consistent
  with the outcome of the original experiments.}
